\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{hyperref}

\title{Perfect Closure and Zeta Zeros: The Critical Line as a Square-Root Mirror}
\author{John Van Geem / RQM Technologies}
\date{April 2026}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}

\begin{document}
\maketitle

\begin{abstract}
We formalize a zeta-specific notion of \emph{Perfect Closure} and isolate a rigorous local statement: for each prime route, the critical line $\Re(s)=\tfrac12$ is the unique amplitude-balance line. We then extend this to finite prime sets and define a global completed-zeta residual $C(t)=|\Xi(t)|^2$ with $\Xi(t)=\xi(\tfrac12+it)$. Zeros of $\Xi$ are interpreted as global closure events in this framework. No proof of the Riemann Hypothesis is claimed.
\end{abstract}

\section{Introduction}

This note develops a constrained closure formalization for the zeta setting. The aim is to state clean local balance theorems while separating proven statements from interpretation.

\section{Perfect Closure in the zeta setting}

\begin{definition}[Perfect Closure, zeta form]
A \emph{Perfect Closure event} is a vanishing of a designated closure residual constructed from zeta data.
\end{definition}

At local prime level we use imbalance functionals. At global level we use the completed-zeta residual $C(t)=|\Xi(t)|^2$.

\begin{remark}
In this paper, Perfect Closure is a formalization device inside a research program, not a replacement for analytic number theory.
\end{remark}

\section{Three reflections in the critical strip}

Let $s=\sigma+it$. Define
\[
J(s)=\overline{s},\qquad F(s)=1-s,\qquad R(s)=1-\overline{s}=F\circ J=J\circ F.
\]
The map $R$ fixes the critical line:
\[
R\!\left(\tfrac12+it\right)=\tfrac12+it.
\]

\section{Prime routes and the square-root mirror}

For prime $p>1$,
\[
p^{-s}=p^{-\sigma}e^{-it\log p}.
\]
On $\sigma=\tfrac12$,
\[
p^{-(1/2+it)}=\frac{1}{\sqrt p}e^{-it\log p},\qquad
p^{-(1/2-it)}=\frac{1}{\sqrt p}e^{+it\log p}.
\]
Both routes have magnitude $p^{-1/2}$ and opposite phase direction.

\section{Local prime imbalance}

Define
\[
B_p(\sigma)=\left|p^{-\sigma}-p^{-(1-\sigma)}\right|.
\]
With $\sigma=\tfrac12+\delta$,
\begin{align*}
B_p\!\left(\tfrac12+\delta\right)
&=\left|p^{-1/2-\delta}-p^{-1/2+\delta}\right|\\
&=2p^{-1/2}\left|\sinh(\delta\log p)\right|.
\end{align*}

\begin{proposition}
For every $p>1$, $B_p(\sigma)=0$ if and only if $\sigma=\tfrac12$.
\end{proposition}

\begin{proof}
Since $p^{-1/2}>0$,
\[
B_p\!\left(\tfrac12+\delta\right)=0
\iff \sinh(\delta\log p)=0.
\]
Because $\log p\neq 0$ and $\sinh x=0$ iff $x=0$, we obtain $\delta=0$, hence $\sigma=\tfrac12$. The converse is immediate.
\end{proof}

\section{Finite global imbalance}

For primes $p_1<\cdots<p_N$, define
\[
B_N(\sigma)^2=\sum_{j=1}^{N}B_{p_j}(\sigma)^2.
\]

\begin{proposition}
For every finite prime set with $p_j>1$,
\[
B_N(\sigma)=0 \iff \sigma=\tfrac12.
\]
\end{proposition}

\begin{proof}
If $\sigma=\tfrac12$ then each summand is zero. Conversely, if $B_N(\sigma)=0$, all nonnegative summands vanish, so each $B_{p_j}(\sigma)=0$, and Proposition 5 yields $\sigma=\tfrac12$.
\end{proof}

\begin{remark}
This is a finite-prime result and does not prove RH.
\end{remark}

\section{Prime-power echo field}

For $\Re(s)>1$,
\[
\log\zeta(s)=\sum_p\sum_{k\ge 1}\frac{p^{-ks}}{k}.
\]
We call $k=1$ terms primitive routes and $k\ge 2$ terms echo routes. This is used only in the convergence domain.

\section{Completed zeta and global closure residual}

\[
\xi(s)=\frac12 s(s-1)\pi^{-s/2}\Gamma\!\left(\frac s2\right)\zeta(s),
\qquad
\Xi(t)=\xi\!\left(\frac12+it\right),
\]
\[
C(t)=|\Xi(t)|^2.
\]
A Perfect Closure event is $C(t)=0$.

\section{Proven statements versus interpretation}

\textbf{Proven:}
\begin{itemize}
  \item $\Re(s)=\tfrac12$ is the unique local prime-route amplitude-balance line.
  \item For finite prime sets, $B_N(\sigma)=0$ only at $\sigma=\tfrac12$.
\end{itemize}

\textbf{Interpreted:}
\begin{itemize}
  \item Zeta zeros are global Perfect Closure events of the completed-zeta residual.
\end{itemize}

\textbf{Not claimed:}
\begin{itemize}
  \item No proof of RH.
  \item No Euler-product convergence claim on $\Re(s)=\tfrac12$.
  \item No single-prime cancellation claim.
\end{itemize}

\section{Short bridge to Paper 2}

\[
Q=e^{u\phi}=\cos\phi+u\sin\phi,\qquad u^2=-1.
\]
If $\Re(Q)=\tfrac12$, then $\phi=\pi/3$, so
\[
Q^3=-1,\qquad Q^6=1.
\]
Paper 2 studies this as quaternionic closure geometry.

\section*{References}
\begin{enumerate}
  \item B. Riemann, \emph{Ueber die Anzahl der Primzahlen unter einer gegebenen Gr"osse} (1859).
  \item E. C. Titchmarsh and D. R. Heath-Brown, \emph{The Theory of the Riemann Zeta-Function}, 2nd ed., Oxford Univ. Press, 1986.
  \item H. M. Edwards, \emph{Riemann's Zeta Function}, Dover, 2001.
  \item B. Mazur and W. Stein, \emph{Prime Numbers and the Riemann Hypothesis}, Cambridge Univ. Press, 2016.
  \item E. Bombieri, “The Riemann Hypothesis,” Clay Mathematics Institute.
\end{enumerate}

\end{document}
