\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{hyperref}

\title{The Zeta--Mass Closure Operator: Perfect Closure as an Eigenvalue Law}
\author{John Van Geem / RQM Technologies}
\date{April 2026}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}

\begin{document}
\maketitle

\begin{abstract}
We present the operator bridge of the Perfect Closure series. Define
\[
\mathcal A_{\mathbf u}=\mathbf u\left(\rho\frac{d}{d\rho}+\frac12\right),\qquad
\chi_t(\rho)=\rho^{-1/2-\mathbf u t},
\]
with eigenvalue relation $\mathcal A_{\mathbf u}\chi_t=t\chi_t$. Let $\Xi(t)=\xi(\tfrac12+it)$ and $\mathcal Z_{\mathbf u}=\Xi(\mathcal A_{\mathbf u})$. If $\Xi(t_n)=0$, then $\mathcal Z_{\mathbf u}\chi_{t_n}=0$. After scale lift $L_*$, the same eigenvalue appears in mass-shell form,
\[
P\bar P=\left(\frac{\hbar t_n}{L_*}\right)^2,
\qquad
m_n=\frac{\hbar}{cL_*}|t_n|.
\]
Thus the critical line may be interpreted as a complex spectral slice of a broader quaternionic closure-mass-shell structure. This is a formal bridge, not a proof of RH or a particle-mass derivation.
\end{abstract}

\section*{Reader Guide}
This paper is the bridge: it shows how one closure eigenvalue can appear both as a zeta-zero condition and as a mass-shell norm after scaling. Keep the non-claim boundary in view throughout.

\section{Introduction}
Papers 1--3 prepared zeta residuals, quaternionic geometry, and mass-shell norm form. We now connect them through one operator pipeline.

\section{Internal scale space}
Let $\rho>0$ and $y=\log\rho$. Prime phases depend on $\log p$, so dilation in $\rho$ is the natural variable.

\section{Quaternionic closure generator and eigenmodes}
Define
\[
\mathcal A_{\mathbf u}=\mathbf u\left(\rho\frac{d}{d\rho}+\frac12\right).
\]
Set
\[
\chi_t(\rho)=\rho^{-1/2-\mathbf u t}.
\]
Then
\[
\mathcal A_{\mathbf u}\chi_t=t\chi_t.
\]
This introduces closure eigenvalues in the internal scale space.

\section{Zeta closure selector}
Define
\[
\Xi(t)=\xi\!\left(\frac12+it\right),
\qquad
\mathcal Z_{\mathbf u}=\Xi(\mathcal A_{\mathbf u}).
\]
If $\Xi(t_n)=0$, then
\[
\mathcal Z_{\mathbf u}\chi_{t_n}=0.
\]
This is the kernel condition linking zeta-slice zeros to quaternionic closure modes.

\section{Mass-shell lift and resolved scale}
With
\[
\log\rho=\frac{\ell}{L_*},
\]
we obtain
\[
m_n=\frac{\hbar}{cL_*}|t_n|,
\qquad
L_*=t_n\frac{\hbar}{mc}=t_n\bar\lambda_C.
\]
These formulas convert formal eigenvalue scale into physical curvature scale. Calibration remains external.

\section{Biquaternionic mass-shell realization}
Using
\[
P\bar P=m^2c^2,
\]
the lift is
\[
P\bar P=\left(\frac{\hbar t_n}{L_*}\right)^2.
\]
This gives the mass-shell face of the same eigenvalue $t_n$.

\section{Complex Spectral Slices of Quaternionic Mass Shells}
The synthesis is encoded by three aligned conditions:
\begin{align*}
\Xi(t_n)&=0,\\
\Xi(\mathcal A_{\mathbf u})\chi_{t_n}&=0,\\
P\bar P&=\left(\frac{\hbar t_n}{L_*}\right)^2.
\end{align*}
So one eigenvalue has a zeta face and a mass-shell face within this framework.

\begin{remark}
This is a formal bridge. It does not claim that zeta zeros are particles or that known masses are already derived.
\end{remark}

\section{Main theorem}
\begin{theorem}[Closure eigenvalue lift]
If $\mathcal A_{\mathbf u}\chi_{t_n}=t_n\chi_{t_n}$ and $\Xi(t_n)=0$, then
\begin{enumerate}
  \item $\chi_{t_n}\in\ker\Xi(\mathcal A_{\mathbf u})$;
  \item under scale map $L_*$, $m_n=\hbar|t_n|/(cL_*)$.
\end{enumerate}
\end{theorem}

\begin{proof}
First,
\[
\Xi(\mathcal A_{\mathbf u})\chi_{t_n}=\Xi(t_n)\chi_{t_n}=0.
\]
Second, define $k_n=t_n/L_*$ and identify with $k_C=mc/\hbar$.
\end{proof}

\section{Non-claims}
No proof of RH, no claim that zeta zeros are particles, no fixed universal $L_*$ in this paper, and no Standard Model mass derivation.

\section*{References}
\begin{enumerate}
  \item E. C. Titchmarsh and D. R. Heath-Brown, \emph{The Theory of the Riemann Zeta-Function}, 1986.
  \item H. M. Edwards, \emph{Riemann's Zeta Function}, 2001.
  \item S. L. Adler, \emph{Quaternionic Quantum Mechanics and Quantum Fields}, 1995.
\end{enumerate}

\end{document}
