\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{hyperref}

\title{Closure Spectra and Physical Calibration: From Eigenvalues to Testable Mass Scales}
\author{John Van Geem / RQM Technologies}
\date{April 2026}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}

\begin{document}
\maketitle

\begin{abstract}
This paper provides the calibration and falsifiability layer for the Perfect Closure series. The formal bridge $m_n=\hbar|t_n|/(cL_*)$ becomes predictive only if $L_*$ is independently fixed or stably shared across a predeclared physical family. We define resolved closure triples, calibration regimes, ratio and stability tests, and falsification criteria.
\end{abstract}

\section{Introduction}
Papers 1--4 established a formal bridge from zeta closure modes to mass-shell expressions. This paper asks when that bridge is predictive.

\section{Recap of the formal bridge}
\[
k_n=\frac{t_n}{L_*},\qquad k_C=\frac{mc}{\hbar},\qquad m_n=\frac{\hbar|t_n|}{cL_*}.
\]

\section{Derivation of \texorpdfstring{$L_*$}{L*}}
From $t_n/L_*=mc/\hbar$,
\[
L_*=\frac{t_n\hbar}{mc}=t_n\bar\lambda_C,
\qquad
\bar\lambda_C=\frac{\hbar}{mc}.
\]

\section{Resolved closure}
\begin{definition}[Resolved closure triple]
A triple $(t_n,L_*,m_n)$ is resolved if
\begin{itemize}
  \item $\Xi(t_n)=0$,
  \item $A_u\chi_{t_n}=t_n\chi_{t_n}$,
  \item $P\bar P=m_n^2c^2=(\hbar t_n/L_*)^2$.
\end{itemize}
\end{definition}

\begin{remark}
Resolved consistency is not yet predictive sufficiency.
\end{remark}

\section{Calibration regimes}
\begin{enumerate}
  \item Particle-specific $L_*$ (weak predictive content).
  \item Family-specific $L_*$ (intermediate, testable).
  \item Universal $L_*$ (strongest, most falsifiable).
\end{enumerate}

\section{Ratio tests}
If $L_*$ is shared,
\[
\frac{m_a}{m_b}=\frac{t_m}{t_n}.
\]
Assignments must be predeclared and uncertainty-aware.

\section{Scale-stability tests}
Compute
\[
L_*(\mathrm{particle},n)=\frac{\hbar t_n}{m_{\mathrm{particle}}c}.
\]
Stability/clustering across a family is required for credibility.

\section{Avoiding curve fitting}
Failure modes: post hoc reassignment, many adjustable parameters, tolerance inflation, coincidence-only ratios.

\section{Mechanism requirement}
A predictive theory needs independent dynamics that explain subset choice and scale fixing, plus observables beyond mass fitting.

\section{Evidence and falsification}
\textbf{Evidence:} predeclared stable $L_*$, successful withheld-mass prediction, independent dynamical corroboration.\\
\textbf{Falsification:} no stable $L_*$ in natural families, only post hoc fits, no independent mechanism, no new predictions.

\section{Conclusion}
Perfect Closure becomes physical only when closure eigenvalues map to stable Compton-scale curvature through independently justified $L_*$.

\section*{References}
\begin{enumerate}
  \item K. G. Wilson, “The renormalization group and critical phenomena,” \emph{Rev. Mod. Phys.} 55 (1983).
  \item R. P. Feynman, \emph{QED: The Strange Theory of Light and Matter}, 1985.
  \item S. L. Adler, \emph{Quaternionic Quantum Mechanics and Quantum Fields}, 1995.
\end{enumerate}

\end{document}
